### 2013-07-05 Tex/chapters/results.tex
Einleitung zu Binder Werten bei Tc: g*

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
per site \(E=\frac{1}{N}\hat H\) are calculated and saved for every
\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
(see also \ref{ssec:eqtime}). The used values for different system sizes
are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
the \(t_{eq}\) values are generously rounded up to be on the safe side
and the \(\tau\) values are determined as the maximum \(\tau\) over all
simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
and rounded up to the next integer.
\begin{table}[htbp]
    \center
    \begin{tabular}{l r r r r r}
        \toprule
        \(L\)    & 16 &  32 &  64 & 128 & 256\\
        \midrule
        \(\tau\) &  3 &   5 &   7 &  12 &  16\\
        \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
        \bottomrule
    \end{tabular}
    \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
    \label{tab:tauAndTeq}
\end{table}\\
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
calculated sweeps totals to
\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
The expected values \(\avg{O}\) for \(100\) different random proximity
graphs with the same disorder parameter \(\sigma\) are then averaged to
\(\overline{\avg{O}}\). Not only the seed to generate the new random
realization of the proximity graph gets changed, but also the seed for
the random numbers used in the Monte Carlo simulation and during the
generation of the random start configuration of the spins.\\
The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
\cite{Bootstrap} with 200 bootstrap samples if not noted otherwise.
Note that while \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
\(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
over different realizations of the random proximity graph, which are
surely uncorrelated.
Because every error mentioned in this thesis is of this type, it is not
necessary to determine \(\tau\) for each observable. Therefore a good
error estimate can be achieved by simple bootstrapping. Though one has
to simulate enough uncorrelated states for each realization, to keep
the \(\Delta \overline{\avg{O}}\) small.

\subsection{Short Analysis of the Autocorrelation Time  $\tau$}
    % Sollte das hier rein?
    Before the results are presented, a short analysis of the
    autocorrelation time \(\tau\) is given, to illustrate the benefits
    of the used Wolff cluster algorithm.\\
    In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
    the autocorrelation time for the magnetization per site \(m\) at \(\sigma=0\) is plotted.
    \begin{figure}[htbp]
        \centering
        \subfigure[in dependence on the temperature $T$][]
        {
            \label{fig:autocorr:temperatures}
            \includegraphics[width=0.45\textwidth]{plots/autocorrT}
        }
        \subfigure[in dependence on the system size $L$][]
        {
            \label{fig:autocorr:powerLaw}
            \includegraphics[width=0.45\textwidth]{plots/autocorrL}
        }
        \caption[The autocorrelation time $\tau$]
        {
            Dependece of the autocorrelation time $\tau$ on
            \subref{fig:autocorr:temperatures} the temperature $T$ for
                $\sigma=0$ and
            \subref{fig:autocorr:powerLaw} the system size $L$ (errorbars
                are the standard error determined by bootstrapping)
        }
        \label{fig:autocorr}
    \end{figure}
    The plateau at low temperatures is easy to understand considering the
    effects of the Wolff algorithm. At low temperatures it flips nearly every
    spin in every step, thus the correlation drops to zero after one sweep.
    Alternatively the parallel tempering algorithm swaps spin configurations
    with possibly different signs, thus having the same effect.
    Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
    temperature. The cause is probably the effectiveness of the Wolff cluster
    algorithm at \(T_c\).
    Obviously the autocorrelation time \(\tau\) increases with the system
    size. In fact it obeys a power law, which is the expected behaivior of
    a dynamical critical exponent \(z\) as mentioned in section \ref{ssec:eqtime}.
    In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
    over \(L\) and the dynamical exponent \(z'\) is determined as \(z'=0.64(2)\).
    This exponent is much higher than the one of Wolff cluster
    algorithm at criticality, which is \(z=0.25\)\cite{NewmanBarkema1999}.
    So it represents the dynamical exponent for parallel tempering with
    Metropolis above criticality and thus is not exactly a critical exponent.
    Nevertheless it is interesting, that it obeys a power law just the same.
    Anyhow it is a proof for the effectiveness of the Wolff cluster algorithm
    at criticality.

@@

    \(\sigma\). At \(T_c\) the mean absolute magnetization \(\avg{|m|}\) of

@@

    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}
    it is easy to see that the jump of \(\avg{|m|}\)
    occurs at lower temperatures \(T\) for higher

@@

    decline. The jump is only present in infinite systems, hence no
    computer simulation will show the exact behavior in the
    thermodynamic limit. It will always show some \emph{finte size effects}.

@@

    transition. This is stronger for smaller system sizes, as is visible

@@

    Studies on random lattices with\cite{Lima2000} and without\cite{Janke1994}
    varying coupling constants \(J\) suggest, that the
    critical exponents should not be influenced by the disorder parameter

@@

    comparison with the known exact values \cite[S. 59]{Pelissetto2002}.\\

@@

    For a more in depth look at finite size scaling, \cite{Norrenbrock2011}
    offers a explanation.

@@

    \eqref{eq:fsscaling:g} apply.

@@

        g          &= \frac{3}{2}\brac{1-\frac{\avg{m^4}}{3\avg{m^2}^2}} \propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}

@@

    Where \(g\) from eq. \eqref{eq:fsscaling:g} is a normalized

@@

    are unknown scaling functions. To find the exponents

@@

    collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}\footnote{Examples for a collapse to determine the other critical exponents are in appendix \ref{appendix:finiteSizeScaling}}.

@@

    way with an error estimate, the program

@@

        \subfigure[Example of a Binder cumulant to determine the critical temperature][]

@@

        \subfigure[Example of a datacollapse to determine critical exponents][]

@@

    Because  the magnetization \(m\) is only measured for discrete values
    of \(T\), \(g\) is also only known for these discrete values and has
    to be interpolated to find a intersection. Therefore a cubic spline
    interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}

@@

    Cubic spline interpolation is a piece wise fitting of polynoms of
    degree three which are joined under the condition to be at least two
    times continuously differentiable.

@@

\subsection{Critical Temperature}
\label{ssec:binderIntersections}
    The evaluation of the Binder cumulant's intersections, yields the
    critical temperatures \(T_c\).
    In this section these \(T_c\) on either the Relative Neighborhood
    graph or the Gabriel graph are compared. In the following figures,
    the Relative Neighborhood graph will always be on the left side
    and the Gabriel graph on the right side.
    In fig. \ref{fig:Tc} \(T_c\) is plotted over \(\sigma\).
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:Tc:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc}
        }
        \subfigure[][]
        {
            \label{sfig:Tc:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc}
        }
        \caption[Critical Temperature over different disorder parameters]
        {
            Critical temperatures \(T_c\) over different
            disorder parameters \(\sigma\) for
            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc:GG} the Gabriel Graph.\\
        }
        \label{fig:Tc}
    \end{figure}\\
    One sees that the Relative Neighborhood graph on the left has
    generally a lower critical temperature than the Gabriel. Also \(T_c\)
    of the Relative Neighborhood graph decreases
    monotonically while \(T_c\) of the Gabriel rises at first.
    For big \(\sigma\) the displaced nodes approach the limit of randomly
    distributed nodes, hence \(T_c\) is independent of \(\sigma\) for
    \(\sigma >> 1\).\\
    A strange property is the jump from \(\sigma = 0\) to \(\sigma > 0\)
    of \(T_c\) on the Gabriel graph. To understand that, one has to
    consider the influence of the graph properties on the critical
    temperature.\\
    A characteristic property of a graph is it's degree \(K\).
    The degree \(K\) of a graph -- sometimes called \emph{coordination number} --
    is defined as the mean count of neighbors per node
    \begin{equation}
        K = \frac{\sum_{\avg{i,j}} 1}{\sum_{i} 1}
        \label{eq:degree}
    \end{equation}
    Therefore the degree of the graphs at different \(\sigma\) is
    plotted in fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:deg:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_deg}
        }
        \subfigure[][]
        {
            \label{sfig:deg:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_deg}
        }

        \subfigure[][]
        {
            \label{sfig:Tc_norm_deg:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg}
        }
        \subfigure[][]
        {
            \label{sfig:Tc_norm_deg:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg}
        }

        \caption[Critical Temperature normalized by Degree of the Graph]
        {
            Top: Degree \(K\) of graph over different
            disorder parameters \(\sigma\) for
            \subref{sfig:deg:RNG} the Relative Neighborhood Graph and
            \subref{sfig:deg:GG} the Gabriel Graph.\\
            Bottom: Critical temperatures normalized by degree over different
            disorder parameters for
            \subref{sfig:Tc_norm_deg:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc_norm_deg:GG} the Gabriel Graph.
        }
        \label{fig:Tc_deg}
    \end{figure}\\
    \(T_c\) and \(K\) are evidently correlated. This is not
    unexpected. For example the Honeycomb lattice is of degree \(K=3\)
    and for which exists an analytic solution \cite{Wannier1945}.
    It has a critical temperature of
    \begin{equation}
        \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52
        \label{eq:exactHCTc}
    \end{equation}
    This is lower than for the square lattice with degree 4.\\
    It seems reasonable to normalize \(T_c\) by the degree of the underlying
    graph. This is done in fig \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
    Indeed the normalization eliminates the jump and reduces the
    slope of the rising on the Gabriel graph. Hence it reduces differences
    between the Relative Neighborhood graph and the Gabriel graph.\\
    % Zitat, dass Janke das auch gemacht hat .. nochmal nachlesen
    The jump of \(K\) and therefore the jump of \(T_c\) on the Gabriel graph is easily explained
    by the definition of the Gabriel graph and it's aftereffects for
    the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
    a small change of sigma causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
    To fully understand this, take four nodes forming a square. The edge
    across does not exist, because the other two nodes are on the edge
    of the lune. Moving one node slightly into the square, causes the lune
    to get smaller, hence no other nodes are inside or on the edge of
    the lune anymore and the edge appears.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:GG_sigma:zero}
            \includegraphics[width=0.40\textwidth]{images/GG/sigma_e0}
        }
        \subfigure[][]
        {
            \label{sfig:GG_sigma:notzero}
            \includegraphics[width=0.40\textwidth]{images/GG/sigma_g0}
        }
        \caption[Anomaly of the Gabriel graph for small $\sigma$]
        {
            Gabriel graph with periodic boundary conditions for
                \subref{sfig:GG_sigma:zero} \(\sigma = 0\)
                \subref{sfig:GG_sigma:notzero} \(\sigma = 0.01\)
        }
        \label{fig:GG_sigma}
    \end{figure}\\
    But the degree does not alone influence the behavior of \(T_c\).
    Further \(T_c\) depends on the coupling
    constant \(J\), which is obvious in eq. \eqref{eq:exactTc} and
    \eqref{eq:exactHCTc}. Therefore  in fig. \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
    is plotted. This is a number which should combine the dependence on
    the degree and the coupling constant, which is not equal for
    every edge in this case.
    The plots fig \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
    show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:sumJ:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
        }
        \subfigure[][]
        {
            \label{sfig:sumJ:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
        }

        \subfigure[][]
        {
            \label{sfig:Tc_normJ:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_normJ}
        }
        \subfigure[][]
        {
            \label{sfig:Tc_normJ:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_normJ}
        }

        \caption[Critical Temperature normalized by Mean Sum of the Coupling Constants]
        {
            Top: Mean sum of the coupling constants to all
            neighbors over different disorder parameters for
            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
            Bottom: Critical temperatures normalized by mean sum of the
            coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
            disorder parameters for
            \subref{sfig:Tc_normJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc_normJ:GG} the Gabriel Graph.
        }
        \label{fig:TcJ}
    \end{figure}\\
    % I don't know what all that means...
    If one normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
    \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
    jump on the Gabriel graph arises again, but \(T_c\) is now monotonically
    decreasing with increasing disorder parameter \(\sigma\). Moreover
    the forms of both curves are quite similar, but the
    one for the Relative Neighborhood graph \ref{fig:TcJ}\subref{sfig:Tc_norm:RNG}
    is generally lower and spans over a bigger temperature range than
    the curve of the Gabriel graph \ref{fig:TcJ}\subref{sfig:Tc_norm:GG}.
    % Warum??? Die eigenschaften des Graphen sollten mit der Normalisierung erledigt sein.
    % RNG: laengere Kanten -> weniger lokale effekte?
    Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
    disorder has little influence on this normalized critical temperature.
    Also both graph types have a steep decline after the plateau before
    they approach an asymptotic limit for \(\sigma >> 1\)\\\\

    %~ But once the degree of
    %~ the graph and hence the mean sum of the coupling constants decreases,
    %~ the normalized critical temperature decreases, too.\\
    %~ In conclusion the critical temperature depends on the averaged sum
    %~ of the coupling constant \(\avg{\sum_{\avg{i,j}} J_{ij}}\). But after
    %~ normalizing it with this, the plots for both proximity graphs look
    %~ similar.
    % The author is not sure what it means.

\subsection{Critical Exponents}
    For \(\sigma \in \{0,0.1,0.2,0.3,0.5,1.0\}\) a finite size scaling analysis was
    performed to determine the critical exponents \(\beta, \gamma, \nu\)
    using \texttt{autoscale.py} \cite{autoscale2009}. The values for
    \(\sigma = 0\) are analytically known \cite{Pelissetto2002}. The
    values for all other \(\sigma\) should be the same as for \(\sigma = 0\)
    like mentioned before in section \ref{ssec:finitesize}.
    The values for \(\sigma\) are chosen to represent every interesting
    region from fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}:
    the plateau at small \(\sigma\), the steep decline and the plateau at
    big \(\sigma\).\\
    Like in tab. \ref{tab:critExp} to see, most values
    are matching the expectations. Most \(\beta\) seem to be a bit too
    big, but they are close enough to the expectations to be explained
    by the fact that small systems (\(L=32,64\)) were used for the
    analysis.
    Anyway, two critical exponents are sufficient to determine the universality
    class. Therefore this disordered Ising model is in the same universality
    class as the standard Ising ferromagnet \cite[p. 145]{Katzgraber2011}.
    \begin{table}[htbp]
        \center
        \begin{tabular}{l l l l l}
            \toprule
             & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\
            \midrule
            exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(-\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\
            \midrule
            Gabriel      & 0.0 & 1.008(4) & -1.735(2) & 0.1262(4)\\
                         & 0.1 & 1.02(1)  & -1.744(5) & 0.133(6) \\
                         & 0.3 & 1.000(5) & -1.724(16)& 0.129(12)\\
                         & 0.5 & 1.009(8) & -1.750(12)& 0.125(13)\\
                         & 1.0 & 1.015(22)& -1.743(17)& 0.123(16)\\
            \midrule
            Relative N.  & 0.0 & 1.007(2) & -1.740(2) & 0.130(1) \\
                         & 0.1 & 0.99(1)  & -1.746(5) & 0.133(4) \\
                         & 0.2 & 1.022(17)& -1.756(14)& 0.123(10)\\
                         & 0.5 & 1.002(17)& -1.750(16)& 0.143(13)\\
                         & 1.0 & 1.011(20)& -1.758(16)& 0.138(13)\\
            \bottomrule
        \end{tabular}
        \caption{Critical exponents for different $\sigma$}
        \label{tab:critExp}
    \end{table}

\subsection{Critical Value of the Binder Cumulant}
    The value of the Binder cumulant at the critical point \(g_c\) is
    depends strongly on boundary conditions but only weakly on the lattice
    structure \cite{BinderValue}. For periodic boundary conditions on a
    square lattice it is \(g_c \approx 0.916\) according to \cite{BinderValue}
        \footnote{Note that \cite{BinderValue} uses an other definition of
            the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)
            to match it's definition in this thesis.}.
    Because the analysis of section \ref{ssec:binderIntersections}
    yields \(g_c\) anyway, it is easy to check the consistency and
    behavior of \(g_c\) in the disordered Ising model.\\
    \begin{figure}[htbp]
        \centering
        \subfigure[for a Relative Neighborhood graph][]
        {
            \label{sfig:TcG:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_TcG}
        }
        \subfigure[for a Gabriel graph][]
        {
            \label{sfig:TcG:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_TcG}
        }
        \caption[Values of the Binder cumulant at the critical point $g_c$]
        {
            Values of the Binder cumulant at the critical point \(g_c\)
            for\\
            \subref{sfig:TcG:RNG} a Relative Neighborhood graph and\\
            \subref{sfig:TcG:GG} a Gabriel graph for different \(\sigma\).
            The dotted line is the reference value for square lattices
            with periodic boundary conditions \cite{BinderValue}, which
            corresponds to \(\sigma = 0\).
        }
        \label{fig:TcG}
    \end{figure}\\
    Considering both plots in fig. \ref{fig:TcG}, \(g_c\) is for low
    \(\sigma\) obviously always bigger than the known value. Though the
    deviation is less than \(1\%\). Perhaps this is some inherent flaw
    of the cubic spline interpolation used to acquire these \(g_c\) values.
    For bigger \(\sigma\) the uncertainty gets greater, but the values
    do only differ by a few percent, hence even the big disorder and
    definition of nearest neighbors via a proximity graph does not change
    \(g_c\) much. This is the expected behavior.

>>>>

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
and the magnetisation per site \(m=\frac{1}{N}\sum_i s_i\) and energy
per site \(E=\frac{1}{N}\hat H\) are calculated and saved for every
\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
(see also \ref{ssec:eqtime}).
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(10000\) measurements for \(L=16,32\) or \(5000\) for
\(L=64,128\). The expected values \(\avg{O}\) for \(100\) different
random proximity graphs with the same disorder paramter \(\sigma\)
are then averaged to \(\overline{\avg{O}}\). The errors are estimated
by bootstrapping \cite{Bootstrap}.

@@

    \(\sigma\). At \(T_c\) the mean absolute magnetisation \(\avg{|m|}\) of

@@

    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}
    it is easy to see that the jump occurs at lower temperatures \(T\) for higher

@@

    decline. The jump is only present in infinite systems, hence every
    computer simulation will show some \emph{finte size effects}.

@@

    trasition. This is stronger for smaller system sizes, as is visible

@@

    Studies on random lattices with variing coupling constants \(J\)
    \cite{Lima2000} and without \cite{Janke1994} suggest, that the
    critical exponents should not be influenced by the disorder paramter

@@

    comparision with the known exact values \cite[S. 59]{Pelissetto2002}.\\

@@

@@

    \eqref{eq:fsscaling:g} apply \cite[p. 145f]{Katzgraber2011}.

@@

        g         &\propto \tilde{G}\brac{L^\frac{1}{\nu}\brac{T-T_c}}\\
        \label{eq:binderCumulant}
        g &= \frac{3}{2}\brac{1-\frac{\avg{m^4}}{3\avg{m^2}^2}}

@@

    Where \(g\) from eq. \eqref{eq:binderCumulant} is a normalized

@@

    are unkown scaling functions. To find the exponents

@@

    collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}.

@@

    way with an error estimate, the programm

@@

        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{

@@

        \subfigure[Example of a datacollapse to determine critical exponents][]{

@@

    Therefore a cubic spline interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}

@@

@@

\subsection{Critical Temperature}
\label{ssec:binderIntersections}
    The evaluation of the Binder cumulant's intersections, yields the
    critical temperatures \(T_c\), which are plotted in
    fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}.
    Further in fig. \ref{fig:Tc}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
    is plotted which is evidently correlated with \(T_c\).
    That is plausible, because \(T_c\) is dependend on the coupling
    constant \(J\) (compare \eqref{eq:exactTc}).\\
    It seems reasonable to normalize the values of \(T_{c}\) by
    \(\avg{\sum_{\avg{i,j}} J_{ij}}\) which yields the diagramms fig.
    \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:Tc:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc}
        }
        \subfigure[][]
        {
            \label{sfig:Tc:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc}
        }

        \subfigure[][]
        {
            \label{sfig:sumJ:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
        }
        \subfigure[][]
        {
            \label{sfig:sumJ:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
        }

        \subfigure[][]
        {
            \label{sfig:Tc_norm:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm}
        }
        \subfigure[][]
        {
            \label{sfig:Tc_norm:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}
        }
        \caption[Critical Temperature over different disorder parameters]
        {
            Top: Critical temperatures over different
            disorder parameters for
            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc:GG} the Gabriel Graph.\\
            Middle: Mean sum of the coupling constants to all
            neighbors over different disorder parameters for
            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
            Bottom: Normalized critical temperatures over different
            disorder parameters for
            \subref{sfig:Tc_norm:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc_norm:GG} the Gabriel Graph.
        }
        \label{fig:Tc}
    \end{figure}\\
    % I don't know what all that means...
    The Gabriel graph, which is shown on the right side of fig. \ref{fig:Tc},
    jumps from \(\sigma = 0\) to \(\sigma > 0\). This is easily explained
    by the definition of the Gabriel graph and it's aftereffects for
    the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
    a small change of sigma causes many new egdes to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
    To fully understand this, take four nodes forming a square. The edge
    across does not exist, because the other two nodes are on the edge
    of the lune. Moving one node slightly into the square, causes the lune
    to get smaller, hence no other nodes are inside or on the edge of
    the lune anymore and the edge appears.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:GG_sigma:zero}
            \includegraphics[width=0.40\textwidth]{images/GG/sigma_e0}
        }
        \subfigure[][]
        {
            \label{sfig:GG_sigma:notzero}
            \includegraphics[width=0.40\textwidth]{images/GG/sigma_g0}
        }
        \caption[]
        {
            Gabriel graph with periodic boundary conditions for
                \subref{sfig:GG_sigma:zero} \(\sigma = 0\)
                \subref{sfig:GG_sigma:notzero} \(\sigma = 0.01\)
        }
        \label{fig:GG_sigma}
    \end{figure}\\
    Moreover fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}
    shows monotonically decreasing \(T_c\) with increasing disorder
    parameter \(\sigma\). The forms of both curves are similar, but the
    one for the Relative Neighborhood graph \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}
    is generally lower and spans over a bigger temperature range than
    the curve of the Gabriel graph \ref{fig:Tc}\subref{sfig:Tc_norm:GG}.
    % Warum??? Die eigenschaften des Graphen sollten mit der Normalisierung erledigt sein.
    % RNG: laengere Kanten -> weniger lokale effekte?
    For big \(\sigma\) the curve approaches the limit of randomly
    distributed nodes, hence \(T_c\) is independet of \(\sigma\) for
    \(\sigma >> 1\).\\
    Also both graph types have a plateau at \(0 < \sigma < 0.1\). So
    small disorder has little influence on the normalized critical temperature.
    But once the degree of the graph and hence the mean sum of the coupling
    constants decreases, the normalized critical temperature decreases, too.
    % The author is not sure what it means.
    % mit theo ergebnissen von Honeycomb \cite{Wannier1945} vergleichen (fur deg = 3)
    % cosh(2L_c)=2 mit L_c = J/2kT_c -> T_c \approx 1.52

\subsection{Critical Exponents}
    For \(\sigma \in \{0,0.1,0.2,0.3,0.5,1.0\}\) a finite size scaling analysis was
    performed to determine the critical exponents \(\beta, \gamma, \nu\)
    using \texttt{autoscale.py} \cite{autoscale2009}. The values for
    \(\sigma = 0\) are analytically known \cite{Pelissetto2002}. The
    values for all other \(\sigma\) should be the same as for \(\sigma = 0\)
    like mentioned before in section \ref{ssec:finitesize}.
    The values for \(\sigma\) are chosen to represent every interesting
    region from fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}:
    the plateau at small \(\sigma\), the steep decline and the plateau at
    big \(\sigma\).\\
    Like in tab. \ref{tab:critExp} to see, most values
    are matching the expectations. Most \(\beta\) seem to be a bit too
    big, but they are close enough to the expectations to be explained
    by the fact that small systems (\(L=32,64\)) were used for the
    analysis.
    Anyway, two critical exponents are sufficient to determine the universality
    class. Therefore this disordered Ising modell is in the same universality
    class as the standard Ising ferromagnet \cite[p. 145]{Katzgraber2011}.
    \begin{table}[htbp]
        \center
        \begin{tabular}{l l l l l}
            \toprule
             & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\
            \midrule
            exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(-\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\
            \midrule
            Gabriel      & 0.0 & 1.008(4) & -1.735(2) & 0.1262(4)\\
                         & 0.1 & 1.02(1)  & -1.744(5) & 0.133(6) \\
                         & 0.3 & 1.000(5) & -1.724(16)& 0.129(12)\\
                         & 0.5 & 1.009(8) & -1.750(12)& 0.125(13)\\
                         & 1.0 & 1.015(22)& -1.743(17)& 0.123(16)\\
            \midrule
            Relative N.  & 0.0 & 1.007(2) & -1.739(2) & 0.130(1) \\
                         & 0.1 & 0.99(1)  & -1.746(5) & 0.133(4) \\
                         & 0.2 & 1.022(17)& -1.756(14)& 0.123(10)\\
                         & 0.5 & 1.002(17)& -1.750(16)& 0.143(13)\\
                         & 1.0 & 1.011(20)& -1.758(16)& 0.138(13)\\
            \bottomrule
        \end{tabular}
        \caption{Critical exponents for different \(\sigma\)}
        \label{tab:critExp}
    \end{table}

\subsection{Critical Value of the Binder Cumulant}
    The value of the Binder cumulant at the critical point \(g^*\) is
    depends strongly on boundary conditions but only weakly on the lattice
    structure \cite{BinderValue}. For periodic boundary conditions on a
    square lattice it is \(g^* \approx 0.916\) according to \cite{BinderValue}
        \footnote{Note that \cite{BinderValue} uses an other definition of
            the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)
            to match it's definition in this thesis.}.
    Because the analysis of section \ref{ssec:binderIntersections}
    yields \(g^*\) anyway, it is easy to check the consistency and
    behaivior of \(g^*\) in the disordered Ising modell.\\
    \begin{figure}[htbp]
        \centering
        \subfigure[for a Relative Neighborhood graph][]
        {
            \label{sfig:TcG:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_TcG}
        }
        \subfigure[for a Gabriel graph][]
        {
            \label{sfig:TcG:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_TcG}
        }
        \caption[Values of the Binder cumulant at the critical point $g^*$]
        {
            Values of the Binder cumulant at the critical point \(g^*\)
            for\\
            \subref{sfig:TcG:RNG} a Relative Neighborhood graph and\\
            \subref{sfig:TcG:GG} a Gabriel graph for different \(\sigma\).
            The dotted line is the reference value for square lattices
            with periodic boundary conditions \cite{BinderValue}, which
            corresponds to \(\sigma = 0\).
        }
        \label{fig:TcG}
    \end{figure}\\
